SAT Competition 2020\tnoteref{title}

### 2021-01-28 paper/main.tex

% \begin{equation}
% \label{eq-similarity}
\[
	similarity(S, S') =\quad 1 - \frac{\sum{|S_{i} - S'_{i}|}}{316 \cdot \num{10000}}
\]
% \end{equation}
We calculated the \emph{similarity} of the $30$ solvers with the
best average PAR-2 score in the main track. The results are displayed in
Figure~\ref{fig-similarity-main} as a \emph{heat map}, similar to the visualization in \cite{Balyo:2015:SATRACE}. Additionally, the result
of hierarchically clustering the solvers based on their similarity is
illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
are joined reflects how similar they are. For example, enabling the \emph{trail
  saving} in \solver{CaDiCaL-alluip} has no impact on the runtime, resulting in
a similarity above \num{0.999}. Therefore the two solvers are joined low in the
dendrogram.
% A similar visualization was used for the results of the SAT Race 2015 \cite{Balyo:2015:SATRace}.

@@

\section*{Acknowledgements}
Matti J\"arvisalo was financially supported by Academy of Finland grants 322869 and 328718.
Martin Suda was supported by the ERC Consolidator grant AI4REASON no. 649043 under the EU-H2020 programme,
the Czech Science Foundation project 20-06390Y, and the project RICAIP, no. 857306 under the EU-H2020 programme.

>>>>

% \begin{equation}
% \label{eq-similarity}
\[
	similarity(S, S') =\quad 1 - \frac{\sum{|S_{i} - S'_{i}|}}{316 \cdot \num{10000}}
\]
% \end{equation}
We calculated the \emph{similarity} of the $30$ solvers with the
best average PAR-2 score in the main track. The results are displayed in
Figure~\ref{fig-similarity-main} as a \emph{heat map}, similar to the visualization in \cite{Balyo:2015:SATRace}. Additionally, the result
of hierarchically clustering the solvers based on their similarity is
illustrated as a \emph{dendrogram}. The height at which two solvers or clusters
are joined reflects how similar they are. For example, enabling the \emph{trail
  saving} in \solver{CaDiCaL-alluip} has no impact on the runtime, resulting in
a similarity above \num{0.999}. Therefore the two solvers are joined low in the
dendrogram.
% A similar visualization was used for the results of the SAT Race 2015 \cite{Balyo:2015:SATRace}.

@@

\section*{Acknowledgements}
Matti J\"arvisalo was financially supported by Academy of Finland grants 322869 and 328718.

Martin Suda was supported by the ERC Consolidator grant AI4REASON no. 649043 under the EU-H2020 programme,
the Czech Science Foundation project 20-06390Y, and the project RICAIP, no. 857306 under the EU-H2020 programme.

Nils Froleyks is supported by the Austrian Science Fund (FWF) under projects
W1255-N23, S11408-N23 and by the LIT AI Lab funded by the State of Upper
Austria.
